Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
udpate text regarding the mixing models from Piro

Having examined other possibilities we now consider whether the unusual
properties of \abc\ can be explained simply by invoking strong mixing in the 
SN ejecta. Strong mixing leads to a shorter dark phase than would otherwise
be observed. \textbf{We also consider} whether strong mixing can explain the
rapid, near-linear rise in the light curve.

@@

In Figure~\ref{fig:piro} we compare model calculations from
\citet{2016ApJ...826...96P} to the observed photometry of \abc. The
\citeauthor{2016ApJ...826...96P} models employ a piston driven explosion to
explode a single WD progenitor model. As the piston explosion does not result
in any nucleosynthesis, the distribution of $^{56}$Ni in the ejecta must be
prescribed by hand, which enables a study of the effects of mixing on the
resulting SN emission. Each model employs a fixed $0.5\,\sm$ of $^{56}$Ni
that has been distributed throughout the ejecta via boxcar averaging (see
their Figure~1). The resulting light curves are synthesized using the
SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
shown in Figure~\ref{fig:piro}. Broadly speaking, the results can be
summarized as follows: SN with strong mixing exhibit a rapid almost linear
rise and quickly develop blue colors, whereas models where the $^{56}$Ni is
confined to the innermost layers of the ejecta remain very faint for days
after explosion while exhibiting relatively red optical colors during this
period. The fast rise and blue color of \abc\ are qualitatively consistent
with the strong mixing models from \citet{2016ApJ...826...96P}, as shown in
Figure~\ref{fig:piro}. In fact, if we adopt $t_\mathrm{exp} = t_0 - 0.4 \,
\mathrm{d}$, we find that the model with the strongest mixing (orange line in
Figure~\ref{fig:piro}) provides an excellent match to the $g$-band
observations.

While the models from \citet{2016ApJ...826...96P} provide a good match to the
optical photometric evolution of \abc, they consistently overpredict the flux
in the UV. The models shown in Figure~\ref{fig:piro} also overpredict the
photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
Future modeling efforts may improve the match between the simulations and
observations for \abc.

@@

\subsection{The Emerging Sample of Young SNe Ia}

>>>>

Having examined other possibilities we now consider whether the \textbf{early evolution} of \abc\ can be explained simply by invoking strong mixing in the 
SN ejecta. Strong mixing leads to \textbf{a faster initial rise as well as a more rapid evolution towards blue colors}.

@@

Figure~\ref{fig:piro} compares the models from \citet{2016ApJ...826...96P} to
\abc. The \citeauthor{2016ApJ...826...96P} models employ a piston driven
explosion to explode a single WD progenitor model. As the piston explosion
does not result in any nucleosynthesis, the distribution of $^{56}$Ni in the
ejecta must be prescribed by hand, which enables a study of the effects of
mixing on the resulting SN emission. Each model employs a fixed $0.5\,\sm$ of
$^{56}$Ni that has been distributed throughout the ejecta via boxcar averaging
(see their Figure~1). The resulting light curves are synthesized using the
SuperNova Explosion Code (\texttt{SNEC}; \citealt{2015ApJ...814...63M}), as
shown in Figure~\ref{fig:piro}. Broadly speaking, the results can be
summarized as follows: SNe with strong mixing exhibit a rapid rise and quickly
develop blue colors, whereas models where the $^{56}$Ni is confined to the
innermost layers of the ejecta remain faint for days after explosion and
\textbf{feature a gradual color evolution from the red to the blue. The model
with the strongest mixing (dark, long-dashed line in Figure~\ref{fig:piro})
best matches the observations of \abc. This is the only model we have found
that exhibits a flat $(B-V)_0$ color evolution in the days after explosion,
however, in detail this model is too red relative to the observations of \abc.
}

While the models from \citet{2016ApJ...826...96P} provide a good match to the
optical photometric evolution of \abc, they consistently overpredict the flux
in the UV. \textbf{They} also overpredict the
photospheric velocity of \abc\ by $\sim$2--3,000$\; \mathrm{km \; s}^{-1}$.
Future modeling efforts may improve the match between the simulations and
observations for \abc.

@@

\section{\textbf{Discussion: The Emerging Sample of Young SNe Ia}}
